Final Report

### 2022-05-10 Final Report.Rmd
next slides

***
We selected a high population from each continent and used the formula below to determine the low population.

Low population = high population * .10

  - We wanted to have a consistent variation between our selection of low and high populated countries. 
  - Based on our calculation we selected the low populated country that was closest to 10% of the high populated country.
  - EX: U.S (high populated) = 331002651. If we multiply by .10 we get 33100265.1 and Canada (low populated) was a population of 37742154 which was closest to 10% of the US population in 2020

@@

@@

Combine the data based on continent.

@@

@@

ggplot(data=joined_low, aes(x=year, y=Count, color=country, size = total_deaths/Count)) +
  geom_line() +
  labs(title="Percentage of Death Count in Low Population Countries", subtitle="Bar width is equal to percentage of Deaths")+
  xlab("Year")+
  ylab("Population")
```

>>>>

***
We selected a high-population and a low-population country from each continent, but we wanted a consistent variation between our selection of low and high population countries. So, we came up with a formula for calculating what the low-population country should be by multiplying the high-population country by .10. For example, when we chose the U.S (which had a population of 331002651 at the time the data was recorded), we multiplied this number by .10 to get 33100265.1 and find the country whose population most-closesly matched (in this case it was Canada with 37742154).

We purposefully left out countries whose population numbers were higher than the majority because we didn't want those countries to skew the data (Russia, India, and China).

@@

Continents:

North America: U.S, Canada
South America: Brazil, Chile
Africa: Nigeria, Malawi
Europe: Germany, Serbia
Asia: Pakistan, Sri Lanka
Oceania: Australia, New Zealand

@@

We also looked at how the data varied by continent.

@@

This graph shows the population change over time. Something to note is Germany and Australia's line seem relatively flat, but a closer look will determine there is a gradual increase that is drastically slower than the other countries.

@@

ggplot(data=joined_low, aes(x=year, y=Count, color=country, size = total_deaths/Count)) +
  geom_line() +
  labs(title="Percentage of Death Count in Low Population Countries", subtitle="Bar width is equal to percentage of Deaths")+
  xlab("Year")+
  ylab("Population")
```
These graphs are of the same information but we have added the percentage of air-pollution related deaths as the width of the line to demonstrate visually if deaths increased or decreased over time. It is easier to see in the high-populated countries but air-pollution related deaths do decrease over time.
